% Jiani Chen
% Data Science Decal, Spring 2019
% Project 1: Resume Repo
% This project is to write a resume using LaTex. 
%
% Due: Wednesday, February 20th, by 10pm.


\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jiani Chen} % Your name
\address{(415)9xx-xxxx \\ jianichen.jan@gmail.com} % Your phone number and email
\address{San Francisco, 94133  }% Your address

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of California, Berkeley} \hfill {\em June 2018 - Present} 
\\ Bachelor of Physics\\
   {\it Relevant Coursework: \\
   -Numerical Analysis \\
   -Computational Techniques and Data Science in Physics \\
   -Advanced Instrumental Laboratory}\\
{\bf City College of San Francisco} \hfill {\em August 2015 - May 2018} 
\\ Associates of Physics and Associates of Mathematics\hfill
\\ AGS Honors Society
\\ {\it Relevant Coursework: \\
   -Introduction to C++ Programming \\
   -Python Programming }\\
   
\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{Berkeley Institute of Data Science, UC Berkeley}{\em January 2019 - Present}{Undergraduate Research Assistant}{}
\item Optimize Monte-Carlo simulation code to run faster on the Cori supercomputer
\item Reformat data output into most optimal binary format. 
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	CAREER OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Carrier Objective}

Physics major currently attending UC Berkeley. Aiming to leverage technical, problem-solving, and creative thinking skills in a mentally stimulating and challenging work environment.

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages \ & Proficiency in Python, C++, SQL,  \\
Software \& Tools & MS Office, Latex, Matlab, Linux\\
Languages \ & Fluent Chinese (Cantonese), Beginner Japanese  \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{City College of San Francisco, San Francisco}{August 2016 - May 2018}{Physics Tutor}{}
\item Developed studying strategies with students along with University level Physics homework tutoring.
\end{rSubsection}

\begin{rSubsection}{City College of San Francisco, San Francisco}{August 2017 - May 2018}{Teaching Assistant}{}
\item Graded weekly homework assignments for a total of 100 students. Provided students with constructive feedback on assignments.
\end{rSubsection}

\begin{rSubsection}{Walgreen's, San Francisco}{February 2015 - January 2016}{Sales Associate}{}
\item Provided customer service, maintained store by ordering and restocking products, and kept cleanliness and organization of store.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------

\begin{rSection}{Extra-Curricular} \itemsep -3pt

\item Volunteer - AGS Honors Society at City College of San Francisco
\item Educational Program Intern - 826 Valencia, San Francisco
\item Art Curator - San Francisco Skate Club
\item Community Volunteer - Thrive House Foundation
\item Program Development Intern - StreetSide Stories Youth Program

\end{rSection}

%----------------------------------------------------------------------------------------

\begin{rSection}

\centering \em References available upon request.

\end{rSection}

\end{document}